% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}
\setlength{\textheight}{11.5in} % increase text height to fit on 1-page 
\topmargin -0.7in
\oddsidemargin -0.3in
\begin{document} 

\name{Eric Stratmann\\[11pt]}

\address{\bf 144 Ayrshire Farm Ln Apt \#103\\Stanford, CA 94305\\estrat@cs.stanford.edu\\(203) 645-9982\\\url{http://github.com/ericstratmann}}
\address{}
                                  
\begin{resume}
  
\section{EDUCATION}          
Stanford University (2008 - Present) \\
Master of Science (2011) \\
PhD Candidate (2008 - Present)\\
Advisor: John Ousterhout \\
Area of Research: Web Frameworks\\
\\
Simon's Rock College of Bard (2005-2008)\\
Bachelor of Arts, magna cum laude (3.53 GPA)\\
Majors: Computer Science (3.89 GPA) and Mathematics (3.67 GPA)

\section{TECHNICAL EXPERIENCE}

Research on Django extensions at Stanford (2011 - 2012)
\begin{itemize}
    \item { Currently developing a Django module that allows developers to add undo functionality to their Website. It hooks into the Model class to save undo information into a generic undo log class, allowing out of order undo. }
    \item { Wrote a Django module allowing developers to easily support server-side push using MVC.}
\end{itemize}

Fiz, a web framework developed at Stanford. (2009 - 2011)
\begin{itemize}
    \item Fiz was a framework that aimed to raise  the level of web application programming by using a component based approach.
    \item Worked on layout, data management, and different components.
    \item Wrote code in Java and Javascript and wrote unit tests for all code.
\end{itemize}

Samsung: R\&D Intern (Summer 2010)
\begin{itemize}
    \item Developed a Javascript framework and API to automatically synchronize HTML5 localStorage to the cloud with node.js.
\end{itemize}

AlamoFS: A Versioning File System with Support for Non-linear History (2007-2008)
\begin{itemize}
    \item Senior thesis with Honors, Simon's Rock College.
    \item Wrote a userland file system incorporating several concepts from revision control systems. The file system would automatically keep a version for every modification made to a file and kept track of several branches that users could create.
\end{itemize}

Microsoft: Software Development Engineer Intern (Summer 2007)
\begin{itemize}
    \item Researched and implemented features for Microsoft Forefront, an enterprise level security product.
    \item Wrote code and tests in C++.
\end{itemize}

\section{PUBLICATIONS}          

Stratmann, E., Ousterhout, J., and Sammer, M. \emph{Integrating Long Polling With an MVC Framework}. USENIX Conference on Web Application Development, June 2011.

Ousterhout, J. and Stratmann, E. \emph{Managing State for Ajax-Driven Web Components}. USENIX \mbox{Conference} on Web Application Development, June 2010.

Ousterhout, J. et al. \emph{The Case for RAMClouds: Scalable High-Performance Storage Entirely in DRAM}. SIGOPS Operating Systems Review, Vol. 43, No. 4, December 2009.

\section{OTHER EMPLOYMENT}
Stanford (Winter 2008, Spring 2012): TA for CS140 (Operating Systems) and CS142 (Web Applications) \\
AXA Equitable (Summer 2006): IT Intern \\
Simon's Rock College (September 2005 - May 2007): Computer Assistant
\end{resume}
\end{document}
